Mental Wellbeing Pathways

### 2023-05-05 minos/validation/mwb_pathways.Rmd
Small path changes to existing scripts, and added a notebook for investigating interventions

Source utils for some functions.
```{r}
source('R_Scripts/utils.r')
```

@@

```{r}
output.path <- 'Minos/output/default_config/'
baseline.path <- paste0(output.path, 'baseline')
base.path <- get_runtime_subdirectory(baseline.path)

>>>>

Source utils for some functions.
```{r}
source('Minos/minos/utils_datain.R')
```

@@

```{r}
output.path <- 'Minos/output/default_config/'
baseline.path <- paste0(output.path, 'baseline')
base.path <- get_latest_runtime_subdirectory(baseline.path)
